---
title: "Practice3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(MASS)
library(ggplot2)
data(survey)
HeightM <-survey[survey[, "Sex"]=="Male", "Height", drop = FALSE] 
# drop = FALSE on ne veux pas que la matrice se transforme en vecteur

ggplot(HeightM) + aes(x = Height) + geom_histogram(aes( y = ..density..))+  labs(y = "Density", x = "Height")

res <- t.test(HeightM$Height, conf.level = 0.95)
res
```

```{r}
x <- rnorm(50,175,100)
stats <- t.test(x)
confidenceInterval <-stats$conf.int
samples <- matrix(rnorm(1000*50,175,100),1000,50)
#sdSamples <-apply(samples,1,sd)
#meanSamples <-apply(samples,1,mean)

tTestSamples <- apply(samples,1,function(x) t.test(x)$conf.int)
tLengthInterval <- tTestSamples[2,] - tTestSamples[1,]
above<-tTestSamples[2,]>=rep(175,1000)
under<-tTestSamples[1,]<=rep(175,1000)


#t.test(samples)


```

How many times it is in the interval (175)

```{r}
count<-sum(above*under)
```

Mean length

```{r}
meanLength<-mean(tLengthInterval)
```

```{r}
TestMean <- function (N){
  samples <- matrix(rnorm(N*50,175,100),N,50)
  tTestSamples <- apply(samples,1,function(x) t.test(x)$conf.int)
  tLengthInterval <- tTestSamples[2,] - tTestSamples[1,]
  above<-tTestSamples[2,]>=rep(175,N)
  under<-tTestSamples[1,]<=rep(175,N)
  count<-sum(above*under)
  meanLength<-mean(tLengthInterval)
  return(c(count,meanLength))
}
```

Keep the results in a table (with 2 columns) varying sample size from 10 to 500 (by 10). Comment.

```{r}
ans<- apply(matrix(seq(10,500,10)),1,TestMean)
```

```{r}
library(ggplot2)
library(mvtnorm)
bivariateData <- rmvnorm(100,rep(125,2), matrix(c(625,375,375,625),nrow=2,ncol=2))
ggplot(data.frame(bivariateData))+aes(x=X1,y=X2)+geom_point(size=0.5)+stat_smooth()
ggplot(data.frame(bivariateData))+aes(x=X1,y=..density..)+geom_density()
```

```{r}
bivariateData[sample(1:100, 73),1] <- NA
```

For each strategy (deletion, mean imputation, regression imputation, stochastic regression imputation), compute the empirical mean of  y), its standard deviation, the correlation between  x and  y , a confidence interval for  μ  and the width of the confidence interval.

We create a function for computing all that
```{r}
# @{param} data - bivariate input after modifying the NA variables
compute <- function(data){
  meanData <- apply(data,2,mean)[1]
  deviation <- apply(data,2,sd)[1]
  correlation <- cor(data[,1],data[,2])
  confInt<-t.test(data[,1])$conf.int
  width<-confInt[2]-confInt[1]
  return(c(meanData,deviation,correlation,confInt,width))
}
```

Deletion

```{r}
dataNA = !complete.cases(bivariateData)
dataRowsDeleted = bivariateData[!dataNA,]
```

Mean

```{r}
dataMean=bivariateData[,] # We duplicate the data
dataMean[dataNA,1] = mean(dataMean[,1], na.rm = TRUE)
#options(warn=-1)
#for(i in 1:ncol(dataMean)){
#  dataMean[is.na(dataMean[,i]), i] <- mean(dataMean[,i], na.rm = TRUE)
#}
#options(warn=0)
```

With Regression

```{r}
dataFrameRStep <- function(bivariateData){
  dataFrame=data.frame(bivariateData)
  dataFrameR = dataFrame[,]

  lmCoeff<-lm(X1~X2,data=dataFrameR[!dataNA,])

  fromWhichWePredict<-data.frame(dataFrameR[dataNA,]$X2)
  colnames(fromWhichWePredict)<-"X2"

  #data.frame(X=x$X)
  whatWePredict<-predict.lm(lmCoeff,fromWhichWePredict)
  dataFrameR[dataNA,1]=whatWePredict
  return(dataFrameR)
}

dataFrameR <- dataFrameRStep(bivariateData)
```

With stochastic linear regression (residual standard error)

```{r}
dataFrameSStep <- function(dataFrameR){
  dataFrameS= dataFrameR[,]
  dataFrameS[dataNA,1] = dataFrameS[dataNA,1] + rnorm(73,0,summary(lmCoeff)$sigma)
  return(dataFrameS)
}

dataFrameS <- dataFrameSStep(dataFrameR)
```

```{r}
mDelete<-compute(dataRowsDeleted)
mMean<-compute(dataMean)
mRegression<-compute(data.matrix(dataFrameR))
mStochastique<-compute(data.matrix(dataFrameS))
mTotal<-data.frame(rbind(mDelete,mMean,mRegression,mStochastique))
names(mTotal) <- c("mean","sd","cor","low","high","width")
mTotal[["name"]] <- c("mDelete", "mMean", "mRegression","mStochastique")

limits <- aes(ymax = high, ymin=low)
dodge <- position_dodge(width=0.9)
ggplot(mTotal, aes(y=mean,x=name))+geom_bar( stat="identity") + geom_errorbar(limits, position=dodge, width=0.25)
ggplot(mTotal, aes(y=sd,x=name))+ geom_point(size=0.5)

```

We create a function for wrapping all the work

```{r}
computeStats <- function(){
  bivariateData <- rmvnorm(100,rep(125,2), matrix(c(625,375,375,625),nrow=2,ncol=2))
  bivariateData[sample(1:100, 73),1] <- NA
  dataNA = !complete.cases(bivariateData)
  #Delete
  dataRowsDeleted = bivariateData[!dataNA,]
  #Mean
  dataMean=bivariateData[,] 
  dataMean[dataNA,1] = mean(dataMean[,1], na.rm = TRUE)
  #Regression
  dataFrameR<-dataFrameRStep(bivariateData)
  #Stochastique
  dataFrameS<-dataFrameSStep(dataFrameR)
  mDelete<-compute(dataRowsDeleted)
  mMean<-compute(dataMean)
  mRegression<-compute(data.matrix(dataFrameR))
  mStochastique<-compute(data.matrix(dataFrameS))
  mTotal<-data.frame(rbind(mDelete,mMean,mRegression,mStochastique))
  names(mTotal) <- c("mean","sd","cor","low","high","width")
  mTotal[["name"]] <- c("mDelete", "mMean", "mRegression","mStochastique")
  return(mTotal)
}
```


```{r}
#exemp<-data.frame(x = 1:10,y1 = 11:20, y2 = 31:40, y3 = 21:30)
#xymelt <- melt(exemp, id.vars = "x")
#ggplot(xymelt, aes(x = x, y = value, color = variable)) +theme_bw() +geom_line()+facet_wrap(~ variable)
#ggplot(xymelt, aes(x = x, y = value, color = variable)) +theme_bw() +geom_line()
```


## `stat_bin()` using `bins = 30`. Pick better value with `binwidth`.
## Warning: Removed 13 rows containing non-finite values (stat_bin).